00_datawrangling.Rmd

### 2019-12-19 analysis/00_datawrangling.Rmd
data wrangling

countData <- as.data.frame(countData)
row.names(countData) <- countData$gene ## make gene the row name
countData[1] <- NULL ## make gene the row name
countData <- round(countData) #round all value to nearest 1s place

# replace dashes with periods (to make deseq happy)
colnames(countData) <- gsub('-', '.', colnames(countData))
head(countData,4)

@@

birds <- colData %>%
  select(bird, sex, treatment) %>%
  distinct()

>>>>

countData <- as.data.frame(countData)
row.names(countData) <- countData$gene ## make gene the row name
countData[1] <- NULL ## make gene the row name
countData <- round(countData) #round all value to nearest 1s place
head(countData)

@@

birds <- colData %>%
  select(bird, sex, treatment) %>%
  distinct()
birds
